---
graphics: yes
name: Montaque 
surname: Reynolds, Ph.D
headcolor: 01416f
position: "PhD Candidate, Philosophy"
www: montaque-reynolds.com
email: "montaque.reynolds@slu.edu"
#twitter: montaquereynolds2
github: redapemusic35 
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
header-includes:
  - \definecolor{linkscolor}{HTML}{026dbb}
  - \usepackage{caption}
  - \usepackage{hyperref}
  - \usepackage{colortbl}
  - \arrayrulecolor{white}
  - \hypersetup{colorlinks=true, linkcolor=linkscolor, filecolor=linkscolor, urlcolor=linkscolor, urlbordercolor=linkscolor}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(gsheet)
library(gt)
library(flextable)
```


# Professional Appointments


```{r working-experience}
# Work
gsheet2tbl("https://docs.google.com/spreadsheets/d/1MHDSoiSYE93L9KGdJW-PQYIUbeMzwN-REDoSBjQyOfY/edit?gid=1554751840#gid=1554751840") %>%
  vitae::detailed_entries(what = title, 
                          when = date, 
                          where = institution, 
                          with = location)
```


# Education

```{r education}
# Edu
gsheet2tbl("https://docs.google.com/spreadsheets/d/1MHDSoiSYE93L9KGdJW-PQYIUbeMzwN-REDoSBjQyOfY/edit?gid=1760172285#gid=1760172285") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what = Degree,
                          when = Year,
                          where = Institution, 
                          with = Location, 
                          why,
                          .protect = FALSE)
```


<!-- # Professional Research Experience -->

<!-- \begingroup -->
<!-- \setlength{\parindent}{-0.5in} -->
<!-- \setlength{\leftskip}{0.5in} -->

<!-- ```{r industry-exp} -->
<!-- # Professional Eval/Research Exp -->
<!-- gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=1697117161") %>% -->
<!--   tidyr::fill(-details) %>% -->
<!--   vitae::detailed_entries(what = project, -->
<!--                           when = date, -->
<!--                           where = institution, -->
<!--                           why = details) -->
<!-- ``` -->

<!-- \endgroup -->
<!-- \leavevmode\newline -->

<!-- # Graduate Research Experience -->

<!-- \begingroup -->
<!-- \setlength{\parindent}{-0.5in} -->
<!-- \setlength{\leftskip}{0.5in} -->
<!-- \newcommand{\code}[1]{\texttt{#1}} -->

<!-- ```{r research-experience} -->
<!-- # Graduate Eval/Research Exp -->
<!-- library(tidyverse) -->
<!-- library(gsheet) -->
<!-- gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=144487203") %>% -->
<!--   tidyr::fill(-details) %>% -->
<!--   vitae::detailed_entries(what = project, -->
<!--                           when = date, -->
<!--                           where = institution, -->
<!--                           why = details, -->
<!--                           .protect = FALSE) -->
<!-- ``` -->
<!-- \endgroup -->
<!-- \leavevmode\newline -->

<!-- # Software -->
<!-- \begingroup -->
<!-- \setlength{\parindent}{-0.5in} -->
<!-- \setlength{\leftskip}{0.5in} -->

<!-- ```{r software, results='asis'} -->
<!-- # Software -->
<!-- gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=1692561333") %>% -->
<!--   select(markdown) %>% -->
<!--   mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""), -->
<!--          markdown = str_replace_all(markdown, "Reynolds, M.", "**Reynolds, M.**")) %>% -->
<!--   pull(markdown) -> software -->
<!--   cat(paste(software), sep = '\n\n') -->

<!-- ``` -->


<!-- \endgroup -->
<!-- \leavevmode\newline -->

# Publications

## Peer Reviewed Journal Articles

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

```{r peerreviewed, results='asis'}
# Journal Articles
gsheet2tbl("https://docs.google.com/spreadsheets/d/1MHDSoiSYE93L9KGdJW-PQYIUbeMzwN-REDoSBjQyOfY/edit?gid=0#gid=0") %>%
  filter(category == "peer-reviewed") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Reynolds, M.", "**Reynolds, M.**")) %>%
  pull(markdown) -> peer
  cat(paste(peer), sep = '\n\n')

```

\endgroup
\leavevmode\newline

## Pre-Prints and Unpublished Manuscripts

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

```{r preprint, results='asis'}
# Pre-prints
gsheet2tbl("https://docs.google.com/spreadsheets/d/1MHDSoiSYE93L9KGdJW-PQYIUbeMzwN-REDoSBjQyOfY/edit?gid=1558956454#gid=1558956454") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Reynolds, M.", "**Reynolds, M.**")) %>%
  pull(markdown) -> preprints
  cat(paste(preprints), sep = '\n\n')

```

\endgroup
\leavevmode\newline

<!-- ## Book Reviews -->

<!-- \begingroup -->
<!-- \setlength{\parindent}{-0.5in} -->
<!-- \setlength{\leftskip}{0.5in} -->

<!-- ```{r bookreviews, results='asis'} -->
<!-- # Book Reviews -->
<!-- gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=0") %>% -->
<!--   filter(category == "book review") %>% -->
<!--   select(markdown) %>% -->
<!--   mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""), -->
<!--          markdown = str_replace_all(markdown, "Reynolds, M.", "**Reynolds, M.**")) %>% -->
<!--   pull(markdown) -> bookreviews -->
<!--   cat(paste(bookreviews), sep = '\n\n') -->

<!-- ``` -->

<!-- \endgroup -->
<!-- \leavevmode\newline -->

<!-- ## Technical Reports -->

<!-- \begingroup -->
<!-- \setlength{\parindent}{-0.5in} -->
<!-- \setlength{\leftskip}{0.5in} -->

<!-- ```{r techreports, results='asis'} -->
<!-- # Technical Reports -->
<!-- gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=1473597883") %>% -->
<!--   select(markdown) %>% -->
<!--   mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""), -->
<!--          markdown = str_replace_all(markdown, "Reynolds, M.", "**Reynolds, M.**")) %>% -->
<!--   pull(markdown) -> tr -->
<!--   cat(paste(tr), sep = '\n\n') -->

<!-- ``` -->

<!-- \endgroup -->
<!-- \leavevmode\newline -->

# Conference Papers and Presentations

## International/National Conferences

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}


```{r intlconf, results='asis'}
# Conference Papers and Presentations
gsheet2tbl("https://docs.google.com/spreadsheets/d/1MHDSoiSYE93L9KGdJW-PQYIUbeMzwN-REDoSBjQyOfY/edit?gid=318960497#gid=318960497") %>%
  filter(category == "intl") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Reynolds, M.", "**Reynolds, M.**")) %>%
  pull(markdown) -> intl
  cat(paste(intl), sep = '\n\n')

```

\endgroup
\leavevmode\newline

## Regional Conferences

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

```{r regional, results='asis'}
# Regional Conferences
gsheet2tbl("https://docs.google.com/spreadsheets/d/1MHDSoiSYE93L9KGdJW-PQYIUbeMzwN-REDoSBjQyOfY/edit?gid=318960497#gid=318960497") %>%
  filter(category == "regional") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Reynolds, M.", "**Reynolds, M.**")) %>%
  pull(markdown) -> regional
  cat(paste(regional), sep = '\n\n')

```

\endgroup
\leavevmode\newline

## Poster Presentations

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}


```{r poster, results='asis'}
# Poster Presentations
gsheet2tbl("https://docs.google.com/spreadsheets/d/1MHDSoiSYE93L9KGdJW-PQYIUbeMzwN-REDoSBjQyOfY/edit?gid=318960497#gid=318960497") %>%
  filter(category == "poster") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Reynolds, M.", "**Reynolds, M.**")) %>%
  pull(markdown) -> poster
  cat(paste(poster), sep = '\n\n')

```


\endgroup
\leavevmode\newline

## Service to the Profession

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

```{r dept, results='asis'}
# Campus & Department Talks
gsheet2tbl("https://docs.google.com/spreadsheets/d/1MHDSoiSYE93L9KGdJW-PQYIUbeMzwN-REDoSBjQyOfY/edit?gid=318960497#gid=318960497") %>%
  filter(category == "service") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Reynolds, M.", "**Reynolds, M.**")) %>%
  pull(markdown) -> campus
  cat(paste(campus), sep = '\n\n')

```


\endgroup
\leavevmode\newline

## Invited Talks

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

```{r invited, results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1MHDSoiSYE93L9KGdJW-PQYIUbeMzwN-REDoSBjQyOfY/edit?gid=318960497#gid=318960497") %>%
  filter(category == "invited") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Reynolds, M.", "**Reynolds, M.**")) %>%
  pull(markdown) -> invited
  cat(paste(invited), sep = '\n\n')

```


\endgroup
\leavevmode\newline

## Professional Workshops, Webinars, Trainings, and Courses

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

```{r workshops, results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1MHDSoiSYE93L9KGdJW-PQYIUbeMzwN-REDoSBjQyOfY/edit?gid=318960497#gid=318960497") %>%
  filter(category == "workshops") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Reynolds, M.", "**Reynolds, M.**")) %>%
  pull(markdown) -> workshops
  cat(paste(workshops), sep = '\n\n')

```


\endgroup
\leavevmode\newline
\newpage


# Teaching Experience

## Full-Time Experience

```{r teaching-experience}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1MHDSoiSYE93L9KGdJW-PQYIUbeMzwN-REDoSBjQyOfY/edit?gid=802976282#gid=802976282") %>%
  filter(category=="teaching") %>%
  select(-category) %>%
  tidyr::fill(-details) %>%
  vitae::detailed_entries(where = title, when = dates, what = school, with = location, details)
```


<!-- ## Other Teaching Experience -->

```{r other-teaching-experience}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1MHDSoiSYE93L9KGdJW-PQYIUbeMzwN-REDoSBjQyOfY/edit?gid=802976282#gid=802976282") %>%
  filter(category=="other teaching") %>%
  select(-category) %>%
  tidyr::fill(-details) %>%
  vitae::detailed_entries(where = title, when = dates, what = school, with = location, details)
```

<!-- ## Teacher Training Experience -->

```{r teacher-training-experience}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1MHDSoiSYE93L9KGdJW-PQYIUbeMzwN-REDoSBjQyOfY/edit?gid=802976282#gid=802976282") %>%
  filter(category=="teacher training") %>%
  select(-category) %>%
  tidyr::fill(-details) %>%
  vitae::detailed_entries(where = title, when = dates, what = school, with = location, details)
```

# Awards and Honors

```{r award}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1MHDSoiSYE93L9KGdJW-PQYIUbeMzwN-REDoSBjQyOfY/edit?gid=1320047315#gid=1320047315") %>%
  tidyr::fill(-details) %>%
  vitae::detailed_entries(where = organization,
                          when = date,
                          what = award_name,
                          with = details)
```

# Skills


```{r skills, message=FALSE, warning=FALSE}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1MHDSoiSYE93L9KGdJW-PQYIUbeMzwN-REDoSBjQyOfY/edit?gid=885656894#gid=885656894") %>%
  mutate(category = ifelse(is.na(category), " ", category),
         details = ifelse(is.na(details), " ", details
         )) %>%
  knitr::kable(col.names = NULL, align=c("l","l"), escape = F) %>%
  kableExtra::row_spec(row=2, extra_latex_after = "\\arrayrulecolor{white}") %>%
  kableExtra::column_spec(column = 1, bold = T)
```


\leavevmode\newline

# Current Memberships

```{r results='asis'}
membership <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1MHDSoiSYE93L9KGdJW-PQYIUbeMzwN-REDoSBjQyOfY/edit?gid=1398743395#gid=1398743395") %>%
    pull(organization)
  cat(paste('-', membership), sep = '\n')

```

# Notes

This CV is reproducible. All the source code behind this CV is available on \href{https://github.com/acircleda/CV}{my Github repo}.
